Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-16 ms.tex
fixing introduction, another figure

With the advent of the Planck mission, we have an important opportunity to
revisit foreground predictions in light of their superb data. Brief Planck
background. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example \AKARI. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.

@@

\section{Dust Emission Model}
\label{sec:modeling}
Our model is that of FDS99, which consists of two populations of dust 
grains emitting as MBBs, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

%we actually have 6.1' arcminute smoothing
It is true that we have smoothed the input intensity maps for this study 
to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
\cite{planckdust} maps. However, as is apparent from figure 
\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.

>>>>

The \PLANCK~2013 data release \citep{planck2013} represents an important 
opportunity to revisit foreground predictions in light of their superb, 
relatively artifact-free broadband data covering the entire sky and a broad 
range of frequencies. \cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example \AKARI~140-160$\mu$m. We also 
anticipate the optical depth map we derive will be useful as a comparison for 
extinction estimates based directly upon optical/NIR observations of stars.

@@

\section{Dust Emission Model}
\label{sec:modeling}

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single nside=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the four lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

Our model is that of FDS99, which consists of two populations of dust 
grains emitting as MBBs, but with different temperatures
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

%we actually have 6.1' arcminute resolution
It is true that we have smoothed the input intensity maps for this study 
to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
\cite{planckdust} maps. However, as is apparent from figure 
\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.
